%---- Required Packages and Functions ----

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
% Adjust margins
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
\usepackage[most]{tcolorbox}
\tcbset{
	frame code={}
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

% \renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%
%---- End of Packages and Functions ------

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%
%%%%%% DEFINE ELEMENTS HERE %%%%%%%
\newcommand{\name}{Shashank Agarwal} % Your Name
\newcommand{\phone}{85808-25850} % Your Phone Number
\newcommand{\emaila}{shashankmarch27@gmail.com} %Email 1



\begin{document}
\fontfamily{cmr}\selectfont
%----------HEADING-----------------

\textbf{\huge \name} \\
\vspace{1mm}
{\raisebox{0.0\height}{\footnotesize \faPhone}\ +91-\phone} \hspace{8mm}
\href{mailto:\emaila}{\raisebox{0.0\height}{\footnotesize \faEnvelope}\ {\emaila}} \hspace{8mm}
\href{https://github.com/Witty-Wizard}{\raisebox{0.0\height}{\footnotesize \faGithub}\ {Github}} \hspace{8mm}
\href{https://www.linkedin.com/in/shashank-agarwal-pio/}{\raisebox{0.0\height}{\footnotesize \faLinkedin}\ {LinkedIn Profile}}
\vspace{-3mm}

%-----------EDUCATION-----------
\section{\textbf{Education}}
\resumeSubHeadingListStart
\resumeSubheading
{Punjab Engineering College, Chandigarh}{CGPA: 6.04}
{B.Tech In Electrical Engineering}{2021-Present}
\resumeSubheading
{SGGS Collegiate Public School, Chandigarh}{Percentage: 86.8\%}
{11th and 12th}{2019-2021}
\resumeSubheading
{The Gurukul, Panchkula}{Percentage: 85\%}
{9th and 10th}{2017-2019}
\resumeSubHeadingListEnd
\vspace{-5.5mm}
%

%-----------EXPERIENCE-----------------
\section{\textbf{Experience}}
\resumeSubHeadingListStart
\resumeSubheading
{Statcon Electronics India Limited}{January - June, 2024}
{Embedded Software Internship}{Noida}
\resumeItemListStart
\item{Studied and gained proficiency in PLL (Phase-Locked Loop), Park Clarke Transform, PI (Proportional-Integral) controller, and feedforward control concepts through self-directed learning and online resources.}
\item{Practiced implementing these concepts in MATLAB simulations to understand their practical applications in control systems engineering.}
\item{Explored the Zeigler-Nichols method for PI tuning to optimize controller performance in various control systems applications.}
\item{Demonstrated ability to apply theoretical knowledge to real-world problems, enhancing understanding of electrical engineering principles and advanced control techniques.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{\textbf{Projects}}
\resumeSubHeadingListStart
\resumeProject
{CanSat Ground Station} %Project Name
{Developing a ground station for CanSat using React Vite.} %Project Name, Location Name
{Ongoing} %Event Dates

\resumeItemListStart
\item {Utilizing React Vite to create a web-based ground station interface for receiving and analyzing data from CanSat missions.}
\item {Implementing real-time data visualization and telemetry features to monitor the CanSat's performance during flight.}
\item {Integrating features for data logging, mission planning, and remote control functionalities into the ground station software.}
\item {GitHub repository : \href{https://github.com/Gagan-Space/Cansat-Ground-Station.git}{https://github.com/Gagan-Space/Cansat-Ground-Station}}
\resumeItemListEnd
\vspace{-2mm}

\resumeProject
{Dino Game} %Project Name
{Made a replica of the famous Chrome Dino game} %Project Name, Location Name
{3rd Semester} %Event Dates

\resumeItemListStart
\item {Developed using an ESP8266 Xtensa-based 32 Bit Microcontroller, capable of scoring and storing the highest score in memory.}
\item {Exploration project to showcase the capabilities of the ESP8266 Microcontroller.}
\resumeItemListEnd
\vspace{-2mm}

\resumeProject
{LiPo Charger} %Project Name
{Designed and fabricated a lithium battery charger} %Project Name, Location Name
{3rd Semester} %Event Dates

\resumeItemListStart
\item {Designed and fabricated a LiPo charging circuit using a custom-designed PCB and TP4056 lithium battery charger IC.}
\item {Suitable for embedding in low-power applications powered by lithium polymer cells.}
\resumeItemListEnd
\vspace{-2mm}

\resumeSubHeadingListEnd
\vspace{-5.5mm}

%-----------Technical skills-----------------
\section{\textbf{Technical Skills and Interests}}
\begin{itemize}[leftmargin=0.05in, label={}]
  \small{\item{
        \textbf{Technical Skills}{:Arduino, C++, Analog Electronics, Digital Electronics, PCB Designing, Circuit Simulation, MATLAB, Web Technologies, ROS, Linux} \\
        \textbf{Soft Skills}{: Reverse Engineering, Problem Solving, Team Player, Critical Thinking} \\
        \textbf{Areas of Interest}{: Computers and its history, Operating Systems, Robotics, Control Algorithms, Digital Signal Processing, Image Processing} \\
        \textbf{Languages}{: English, Hindi}\\
        }}
\end{itemize}
\vspace{-16pt}

%-----------Achievements-----------------
\section{\textbf{Achievements}}
\vspace{-0.4mm}
\resumeSubHeadingListStart
\resumePOR{2nd Prize in Electrovis} % Award
{ organised by IEEE PEC student chapter} % Event
{2022} %Event Year

\resumePOR{1st Prize in Robo Race } % Award
{organised by Robotics Society PEC at PECFEST} % Event
{2022} %Event Year
\resumeSubHeadingListEnd
\vspace{-5mm}

%-------------------------------------------
\end{document}